Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
updates
Updates

    \caption{A comparison of Markov Equivalence Class (MEC) learned using Adult
	     Income Dataset \citep{Becker1996} using different causal discovery
	     algorithms and sample sizes. Edge colour represents the sample size
	     used: red ($N=400$), and blue ($N=800$). (a) PC algorithm with a
	     mutual information based CI test, (b) PC algorithm with a
    	     residualization based test \citep{Ankan2023}, (c) Hill Climb Search with
	     Bayesian Information Criterion (BIC) score. The learned model structure varies
             significantly in each case.}
    \label{fig:intro}
\end{figure}

@@

To enable users to apply this method to their own datasets, we developed an
interactive web-based tool (shown in Fig.~\ref{fig:web}) for constructing
models. Users begin by uploading their dataset, which initializes an empty DAG
with nodes corresponding to the dataset\'s variables. They can then specify a
p-value threshold and a measure of association threshold. We use the measure of 
conditional association shown in Appendix~\ref{sec:mixed_association}.

>>>>

    \caption{A comparison of Markov Equivalence Classes (MECs) learned from the Adult
	     Income Dataset \citep{Becker1996} using different causal discovery
	     algorithms and sample sizes. Edge colors represents the sample size
	     used: red for $N=400$, and blue for $N=800$. (a) PC algorithm with a
	     mutual information based CI test, (b) PC algorithm with a
    	     residualization based test \citep{Ankan2023}, (c) Hill Climb Search with
	     Bayesian Information Criterion (BIC) score. The learned model structure varies
             significantly across different algorithms and sample sizes.}
    \label{fig:intro}
\end{figure}

@@

To enable users to apply this method to their own datasets, we developed an
interactive web-based tool (shown in Fig.~\ref{fig:web}) for constructing
models. Users begin by uploading their dataset, which initializes an empty DAG
with nodes corresponding to the dataset\'s variables. They can then specify a
p-value threshold and a measure of association threshold. To make the method
work for mixed data types, we use a measure based on canonical correlations
(Appendix~\ref{sec:mixed_association}).
